\chapter{FLAME Project Related Publications}
\label{appendix:pubs}

Many of following publications can be found on-line
at 
\begin{center}
{\tt http://www.cs.utexas.edu/users/flame/publications/} \\
\end{center}

\section{Books}

\renewcommand\labelenumi{B\theenumi}

\begin{enumerate}
\item
Robert~A. van~de Geijn.
\newblock {\em Using {PLAPACK}: Parallel Linear Algebra Package}.
\newblock The MIT Press, 1997.
\item
Robert~A. van~de Geijn and Enrique S. Quintana-Ort\'{\i}.
\newblock
{\em The Science of Programming Matrix Computations}.
\newblock www.lulu.com/contents/1911788/, 2008.
\end{enumerate}

\section{Dissertations}

\renewcommand\labelenumi{D\theenumi}

\begin{enumerate}
\item
John A. Gunnels.
A Systematic Approach to the Design and Analysis of Linear Algebra Algorithms.
The University of Texas at Austin, Department of Computer Sciences.
Technical Report TR-01-44.
December 2001.
\item
Paolo Bientinesi.
Mechanical Derivation and Systematic Analysis of Correct Linear Algebra
Algorithms.
The University of Texas at Austin, Department of Computer Sciences.
August 2006.
\item
Jack Poulson.
Formalized Parallel Dense Linear Algebra and its Application to the
Generalized Eigenvalue Problem.
Masters Thesis.
The University of Texas at Austin, Department of Aerospace Engineering.
May 2009.
(Supervised by Prof. Jeffrey K. Bennighof)
\end{enumerate}


\section{Journal Articles}

\renewcommand\labelenumi{J\theenumi}

\begin{enumerate}
\item
Enrique~S. Quintana, Gregorio Quintana, Xiaobai Sun, and Robert van~de Geijn.
\newblock A note on parallel matrix inversion.
\newblock {\em SIAM Journal on Scientific Computing}, 22(5):1762--1771, 2001.

\item
John~A. Gunnels, Fred~G. Gustavson, Greg~M. Henry, and Robert~A. van~de Geijn.
\newblock 
FLAME: Formal Linear Algebra Methods Environment.
\newblock {\em ACM Transactions on Mathematical Software}, 
27(4):422-455, December 2001.

\item
Enrique~S. Quintana-Ort\'{\i} and Robert van~de Geijn.
\newblock 
Formal Derivation of Algorithms: The Triangular Sylvester Equation.
\newblock {\em ACM Transactions on Mathematical Software}, 
(29) 2, June 2003.

\item
Paolo Bientinesi, John A. Gunnels, Margaret E. Myers, Enrique S. Quintana-Ort\'{\i}, and Robert van de Geijn.
\newblock
The Science of Deriving Dense Linear Algebra Algorithms.
{\em ACM Transactions on Mathematical Software,} 
31(1):1-26, March 2005.

\item
Paolo Bientinesi, Enrique S. Quintana-Ort\'{\i}, and Robert van de Geijn.
\newblock
Representing Linear Algebra Algorithms in Code: The FLAME APIs. 
{\em ACM Transactions on Mathematical Software}, 31(1):27-59, March 2005.

\item
Brian Gunter and Robert van de Geijn. 
\newblock
Parallel Out-of-Core Computation and Updating of the QR Factorization. 
{\em ACM Transactions on Mathematical Software}, 32(1):60-78, March 2005.

\item
Thierry Joffrain, Tze Meng Low, Enrique S. Quintana-Ort\'{\i}, Robert van de Geijn, and Field Van Zee.
\newblock
On Accumulating Householder Transformations.
{\em ACM Transactions on Mathematical Software,}
 32(2):169-179, 2006.

\item
Gregorio Quintana-Ort\'{\i} and Robert van de Geijn.
\newblock
Improving the Performance of Reduction to Hessenberg Form.
{\em ACM Transactions on Mathematical Software,} 32(2):180-194, 2006.

\item
Kazushige Goto and Robert A. van de Geijn.
\newblock
Anatomy of a High-Performance Matrix Multiplication.
\newblock
{\em ACM Transactions on Mathematical Software},
34(2) Article 12, 25 pages, 2008.

\item
 Field G. Van~Zee, Paolo Bientinesi, Tze~Meng Low, and Robert A. van~de~Geijn. 
\newblock
Scalable Parallelization of FLAME Code via the Workqueuing
Model.
\newblock
{\em  ACM Transactions on Mathematical Software},
34(2):10:1--10:29, March 2008.

\item
Paolo Bientinesi, Brian Gunter,
and Robert van de Geijn.
\newblock
Families of Algorithms Related to the Inversion of a Symmetric Positive
Definite Matrix
\newblock
{\em ACM Transactions on Mathematical Software},
35(1), p. 1--22, 2008.

\item
Kazushige Goto and Robert A. van de Geijn.
\newblock
High-Performance Implementation of the Level-3 BLAS.
\newblock
{\em ACM Transactions on Mathematical Software},
35(1) Article 4, 14 pages, 2009.

\item
Enrique Quintana-Ort\'{\i} and Robert van~de~Geijn. 
\newblock
Updating an LU Factorization with Pivoting.
\newblock
{\em ACM Transactions on Mathematical Software},
35(2) Article 11, 16 pages, 2009.

\item
Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Ort\'{\i},
Robert A. van de Geijn, Field G. Van Zee, and Ernie Chan.
\newblock
Programming Matrix Algorithms-by-Blocks for Thread-Level Parallelism.
\newblock
{\em ACM Transactions on Mathematical Software},
36(3):14:1--14:26, 2009.

\item
Field G. Van Zee, Ernie Chan, Robert van de Geijn,
Enrique S. Quintana-Ort\'{\i}, and Gregorio Quintana-Ort\'{\i}.
\newblock
Introducing: The libflame Library for Dense Matrix Computations.
\newblock
{\em Computing in Science and Engineering},
accepted.  

\end{enumerate}

\section{Conference Papers}

\renewcommand\labelenumi{C\theenumi}

\begin{enumerate}

\item
John~A. Gunnels and Robert~A. van~de Geijn.
\newblock
Formal methods for high-performance linear algebra libraries.
\newblock
In Ronald~F. Boisvert and Ping Tak~Peter Tang, editors,
{\em The Architecture of Scientific Software},
pages 193--210. Kluwer Academic Press, 2001.
\newblock
{Proceedings} of {Working} {Conference} on {Sofware} {Architectures}
for {Scientific} {Computing} {Applications} ({IFIP} {WG} 2.5 {WoCo} 8).

\item
John~A. Gunnels, Greg~M. Henry, and Robert~A. van~de Geijn.
\newblock
A family of high-performance matrix multiplication algorithms.
\newblock
In Vassil~N. Alexandrov, Jack~J. Dongarra, Benjoe~A. Juliano,
Ren\'e~S. Renner, and C.J.~Kenneth Tan, editors,
{\em Computational Science - ICCS 2001, Part I},
Lecture Notes in Computer Science 2073,
pages 51--60. Springer-Verlag, 2001.

\item
John~A. Gunnels, Daniel~S. Katz, Enrique~S. Quintana-Ort\'{\i},
and Robert~A. van~de Geijn.
\newblock
Fault--tolerant high--performance matrix multiplication: Theory and
practice.
\newblock
In {\em Proceedings of the International Conference for Dependable
Systems and Networks (DSN-2001)},
p. 47--56, July 2-4, 2001.

\item
Paolo Bientinesi, John Gunnels, Fred Gustavson, Greg Henry, 
Margaret Myers, Enrique Quintana-Ort\'{\i},
and Robert A. van de Geijn.
\newblock
Rapid Development of High-Performance Linear Algebra Libraries.
\newblock
{\em PARA 2004, LNCS 3732},
p. 376--384, 2005.

\item
Paolo Bientinesi, Sergey Kolos, and Robert A. van de Geijn.
\newblock
Automatic Derivation of Linear Algebra Algorithms with Application
to Control Theory.
\newblock
{\em PARA 2004, LNCS 3732},
p. 385--394, 2005.

\item
Thierry Joffrain, Enrique S. Quintana-Ort\'{\i},
and Robert A. van de Geijn.
\newblock
Rapid Development of High-Performance Out-of-Core Solvers.
\newblock
{\em PARA 2004, LNCS 3732},
p. 413--422, 2005.

\item
Tze Meng Low, Robert van de Geijn, and Field Van Zee.
\newblock
Extracting SMP Parallelism for Dense Linear 
Algebra Algorithms from High-Level Specifications.
\newblock
{\em Proceedings of 2005 ACM SIGPLAN Symposium on Principles and Practices
of Parallel Programming}, 2005.

\item
Ernie Chan, Enrique Quintana-Ort\'{\i}, Gregorio Quintana-Ort\'{\i}, and Robert
van~de~Geijn.
\newblock
SuperMatrix Out-of-Order Scheduling of Matrix Operations
for SMP and Multi-Core Architectures.
\newblock
{\em SPAA'07: Proceedings of the Nineteenth ACM Symposium
on Parallelism in Algorithms and Architectures,}
p. 116--125. 2007.

\item
Bryan Marker, Field Van~Zee, Kazushige Goto, Gregorio Quintana-Ort\'{\i},
and Robert van~de~Geijn.
\newblock
Toward Scalable Matrix Multiply on Multithreaded Architectures.  
\newblock
{\em Proceedings of European Conference on Parallel and Distributed
Computing},
p. 748--757, Rennes, France, August 2007.

\item
Ernie Chan, Field G. Van Zee, Enrique S. Quintana-Ort\'{\i},
Gregorio Quintana-Ort\'{\i}, Robert van~de~Geijn. 
\newblock
Satisfying your Dependencies with SuperMatrix.
\newblock
{\em Proceedings of IEEE Cluster Computing 2007,}
p. 91--99, Austin, Texas, September 2007.

\item
Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Ort\'{\i}, Ernie Chan,
Field G. Van~Zee, and Robert A. van~de~Geijn. 
\newblock
Scheduling of QR factorization algorithms on SMP and multi-core architectures.
\newblock
{\em Proceedings of the 16th Euromicro International Conference on Parallel,
Distributed and Network-Wased Processing},
Toulouse, France, February 2008.

\item
Ernie Chan, Field G. Van~Zee, Paolo Bientinesi, Enrique S. Quintana-Ort\'{\i},
Gregorio Quintana-Ort\'{\i}, and Robert van~de~Geijn.
\newblock
SuperMatrix: A Multithreaded Runtime Scheduling System for Algorithms-by-Blocks.  
\newblock
{\em Proceedings of 2008 ACM SIGPLAN Symposium on Principles and Practices
of Parallel Programming},
p. 123--132, Salt Lake City, Utah, February 2008.

\item
Jeff Diamond, Behnam Robatmili, Stephen W. Keckler, Robert van de
Geijn, Kazushige Goto, Doug Burger.
\newblock
High Performance Dense Linear Algebra on a Spatially Distributed Processor. 
\newblock
{\em Proceedings of 2008 ACM SIGPLAN Symposium on Principles and Practices
of Parallel Programming},
Salt Lake City, Utah, February 2008.

\item
Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Ort\'{\i}, Ernie Chan,
Robert van de Geijn, and Field G. Van Zee.
\newblock
Design of Scalable Dense Linear Algebra Libraries for Multithreaded
Architectures: the LU Factorization.
\newblock
{\em Proceedings of the Workshop on Multithreaded Architectures and
Applications},
Miami, Florida, April 2008.

\item
Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Ort\'{\i}, Alfredo Remon,
and Robert A. van de Geijn.
\newblock
An Algorithm-by-Blocks for SuperMatrix Band Cholesky Factorization.
\newblock
{\em Proceedings of the 8th International Meeting on High Performance
Computing for Computational Science},
Toulouse, France, June 2008. 

\item
Gregorio Quintana-Ort\'{\i}, Francisco D. Igual,
Enrique S. Quintana-Ort\'{\i}, Robert van de Geijn.
\newblock
Solving Dense Linear Systems on Platforms with Multiple Hardware Accelerators.
\newblock
{\em Proceedings of 2009 ACM SIGPLAN Symposium on Principles and Practices
of Parallel Programming},
Raleigh, North Carolina, February 2009.

\item
Robert van de Geijn.
\newblock
Beautiful Parallel Code: Evolution vs. Intelligent Design.
\newblock
{\em Supercomputing 2008 Workshop on Node Level Parallelism for Large Scale
Supercomputers},
Austin, Texas, November 2008. 

\item
Mar\'{\i}a Jes\'us Zafont, Alberto Mart\'{\i}n, Francisco D. Igual,
and Enrique S. Quintana-Ort\'{\i}.
\newblock
Fast Development of Dense Linear Algebra Codes on Graphics Processors.
\newblock
{\em 14th International Workshop on High-Level Parallel Programming Models
and Supportive Environments},
Rome, Italy, 2009.

\item
Mercedes Marqu\'es, Gregorio Quintana-Ort\'{\i},
Enrique S. Quintana-Ort\'{\i}, and Robert van de Geijn.
\newblock
Using Graphics Processors to Accelerate the Solution of Out-of-Core Linear
Systems.
\newblock
{\em 8th IEEE International Symposium on Parallel and Distributed Computing},
Lisbon, Portugal, 2009.

\item
Mercedes Marqu\'es, Gregorio Quintana-Ort\'{\i}, 
Enrique S. Quintana-Ort\'{\i}, and Robert van de Geijn.
\newblock
Solving ``Large'' Dense Matrix Problems on Multi-Core Processors and GPUs.
\newblock
{\em 10th IEEE International Workshop on Parallel and Distributed Scientific and
Engineering Computing (PDSEC'09)},
Rome, Italy, 2009.

\item
Mercedes Marqu\'es, Gregorio Quintana-Ort\'{\i},  
Enrique S. Quintana-Ort\'{\i}, and Robert van de Geijn.
\newblock
Out-of-Core Computation of the QR Factorization on Multi-Core Processors.
\newblock
{\em Proceedings of European Conference on Parallel and Distributed Computing},
Delft, The Netherlands, 2009.

\end{enumerate}

\section{FLAME Working Notes}

\renewcommand\labelenumi{W\theenumi}

\begin{enumerate}
\item
      John Gunnels, Greg Henry, and Robert van de Geijn. Formal
      Linear Algebra Methods Environment (FLAME): Overview. FLAME
      Working Note \#1. The University of Texas at Austin, Department
      of Computer Sciences. Technical Report TR-2000-28. November
      2000.

\item
      John A. Gunnels, Daniel S. Katz, Enrique S. Quintana-Ort\'{\i}, and
      Robert van de Geijn. Fault-Tolerant High-Performance
      Matrix-Matrix Multiplication, FLAME Working Note \#2. The
      University of Texas at Austin, Department of Computer
      Sciences. Technical Report TR-2000-34. December 2000.

\item
      John Gunnels and Robert van de Geijn. Developing Linear Algebra
      Algorithms: A Collection of Class Projects. FLAME Working Note
      \#3. The University of Texas at Austin, Department of Computer
      Sciences. Technical Report TR-2001-19. May 2001.

\item
      John Gunnels, Greg Henry, and Robert van de
      Geijn. High-Performance Matrix Multiplication Algorithms for
      Architectures with Hierarchical Memories. FLAME Working Note
      \#4. The University of Texas at Austin, Department of Computer
      Sciences. Technical Report TR-2001-22. June 2001.

\item
      Enrique S. Quintana-Ort\'{\i} and Robert van de Geijn. Formal
      Derivation of Algorithms: The Triangular Sylvester Equation.
      FLAME Working Note \#5. The University of Texas at Austin,
      Department of Computer Sciences. Technical Report
      TR-2001-35. Sept. 2001. 

\item
      John A. Gunnels. A Systematic Approach to the Design and
      Analysis of Linear Algebra Algorithms.
      Ph.D. Dissertation. FLAME Working Note \#6, The University of
      Texas at Austin, Department of Computer Sciences. Technical
      Report TR-2001-44. Nov. 2001.

\item
      Greg M. Henry. Flexible High-Performance Matrix Multiply via a
      Self-Modifying Runtime Code. FLAME Working Note \#7. The
      University of Texas at Austin, Department of Computer
      Sciences. Technical Report TR-2001-46. Dec. 2001.

\item
      Paolo Bientinesi, John A. Gunnels, Margaret E. Myers, Enrique
      S. Quintana-Ort\'{\i}, and Robert van de Geijn. The Science of
      Deriving Dense Linear Algebra Algorithms. FLAME Working Note
      \#8. The University of Texas at Austin, Department of Computer
      Sciences. Technical Report TR-2002-53. Sept. 2002.

\item
      Kazushige Goto and Robert van de Geijn. On Reducing TLB Misses
      in Matrix Multiplication. FLAME Working Note \#9. The University
      of Texas at Austin, Department of Computer Sciences. Technical
      Report TR-2002-55. Nov. 2002.

\item
      Robert A. van de Geijn. Representing Linear Algebra Algorithms in Code: The FLAME API. FLAME Working Note \#10. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2003-01. Jan. 2003.

\item
      Paolo Bientinesi, Enrique S. Quintana-Ort\'{\i}, and Robert van de Geijn. FLAME@lab: A Farewell to Indices. FLAME Working Note \#11. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2003-11. April 2003.

\item
      Tze Meng Low and Robert van de Geijn. An API for Manipulating Matrices Stored by Blocks. FLAME Working Note \#12. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2004-15. May 2004.

\item
      Thierry Joffrain, Tze Meng Low, Enrique S. Quintana-Ort\'{\i}, Robert van de Geijn, and Field Van Zee. On Accumulating Householder Transformations. FLAME Working Note \#13. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2004-43. Oct 2004.

\item
      Gregorio Quintana-Ort\'{\i} and Robert van de Geijn. Improving the Performance of Reduction to Hessenberg Form. FLAME Working Note \#14. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2004-44. Oct 2004.

\item
      Tze Meng Low, Kent Milfeld, Robert van de Geijn, and Field Van Zee. Parallelizing FLAME Code with OpenMP Task Queues. FLAME Working Note \#15. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2004-50.

\item
      Paolo Bientinesi, Kazushige Goto, Tze Meng Low, Enrique S. Quintana-Ort\'{\i}, Robert van de Geijn, and Field Van Zee. FLAME 2005 Prospectus: Towards the Final Generation of Dense Linear Algebra Libraries. FLAME Working Note \#16. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2005-15.

\item
      Paolo Bientinesi and Robert van de Geijn. Representing Dense Linear Algebra Algorithms: A Farewell to Indices. FLAME Working Note \#17. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2006-10.

\item
      H. Carter Edwards and Robert A. van de Geijn. Application Interface to Parallel Dense Matrix Libraries: Just let me solve my problem! FLAME Working Note \#18. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2006-15.

\item
      Paolo Bientinesi, Brian Gunter, and Robert van de Geijn, Families of Algorithms Related to the Inversion of a Symmetric Positive Definite Matrix. FLAME Working Note \#19. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2006-20.

\item
      Kazushige Goto and Robert van de Geijn. High-Performance Implementation of the Level-3 BLAS. FLAME Working Note \#20. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2006-23.

\item
      Enrique S. Quintana-Ort\'{\i} and Robert van de Geijn. Updating an LU Factorization with Pivoting. FLAME Working Note \#21. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-2006-42.

\item
      Ernie Chan, Marcel Heimlich, Avijit Purkayastha, and Robert van de Geijn. Collective Communication: Theory, Practice, and Experience. FLAME Working Note \#22. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-06-44. September 26, 2006.

\item
      Ernie Chan, Enrique S. Quintana-Ort\'{\i}, Gregorio Quintana-Orti, and Robert van de Geijn. SuperMatrix Out-of-Order Scheduling of Matrix Operations for SMP and Multi-Core Architectures. FLAME Working Note \#23. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-06-67. December 18, 2006.

\item
      Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Orti, Ernie Chan, Field G. Van Zee, and Robert van de Geijn. Scheduling of QR factorization algorithms on SMP and multi-core architectures. FLAME Working Note \#24. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-07-37. July 31, 2007.

\item
      Ernie Chan, Field G. Van Zee, Paolo Bientinesi, Enrique S. Quintana-Ort\'{\i}, Gregorio Quintana-Orti, and Robert van de Geijn. SuperMatrix: A Multithreaded Runtime Scheduling System for Algorithms-by-Blocks. FLAME Working Note \#25. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-07-41. August 22, 2007.

\item
      Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Orti, Ernie Chan, Robert van de Geijn, Field G. Van Zee. Design and Scheduling of an Algorithm-by-Blocks for LU Factorization on Multithreaded Architectures. FLAME Working Note \#26. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-07-50. September 19, 2007.

\item
      Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Orti, Alfredo Remon, Robert van de Geijn. SuperMatrix for the Factorization of Band Matrices. FLAME Working Note \#27. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-07-51. September 24, 2007.

\item
      Bryan Marker. On Composing Matrix Multiplication from Kernels. FLAME Working Note \#28. The University of Texas at Austin, Department of Computer Sciences. Report \#HR-07-32 (honors thesis). Spring 2007. 21 pages.

\item
      Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Orti, Ernie Chan, Field G. Van Zee, and Robert van de Geijn. Programming Algorithms-by-Blocks for Matrix Computations on Multithreaded Architectures. FLAME Working Note \#29. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-08-04. January 15, 2008.

\item
      Sergio Barrachina, Maribel Castillo, Francisco D. Igual, Rafael Mayo, Enrique S. Quintana-Ort\'{\i}. FLAG@lab: An M-script API for Linear Algebra Operations on Graphics Processors. FLAME Working Note \#30. Universidad Jaume I, Depto. de Ingenieria y Ciencia de Computadores. Technical Report ICC 01-02-2008. February 14, 2008.

\item
      Maribel Castillo, Ernie Chan, Francisco D. Igual, Rafael Mayo, Enrique S. Quintana-Ort\'{\i}, Gregorio Quintana-Orti, Robert van de Geijn, Field G. Van Zee. Making Programming Synonymous with Programming for Linear Algebra Libraries. FLAME Working Note \#31. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-08-20. April 17, 2008.

\item
      Gregorio Quintana-Ort\'{\i}, Francisco D. Igual, Enrique S. Quintana-Orti, Robert van de Geijn. Solving Dense Linear Algebra Problems on Platforms with Multiple Hardware Accelerators. FLAME Working Note \#32. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-08-22. May 9, 2008.

\item
      Paolo Bientinesi and Robert A. van de Geijn. "The Science of Deriving Stability Analyses." FLAME Working Note \#33. Aachen Institute for Computational Engineering Sciences, RWTH Aachen. TR AICES-2008-2. November 2008. 

\item
      Robert van de Geijn. "Beautiful Parallel Code: Evolution vs. Intelligent Design." Presented at Supercomputing 2008 Workshop on Node Level Parallelism for Large Scale Supercomputers, Austin, Texas, November 2008. FLAME Working Note \#34. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-08-46. Nov. 21, 2008.

\item
      Richard Veras, Jonathan Monette, Enrique Quintana-Ort\'{\i}, and Robert van de Geijn. "FLAMES2S: From Abstraction to High Performance." FLAME Working Note \#35. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-08-49. Dec. 14, 2008. 

\item
      Mercedes Marqu\'es, Gregorio Quintana-Ort\'{\i}, Enrique S. Quintana-Ort\'{\i}, and Robert van de Geijn. "Solving ``Large'' Dense Matrix Problems on Multi-Core Processors and GPUs" FLAME Working Note \#36. Universidad Jaume I, Depto. de Ingenieria y Ciencia de Computadores. Technical Report ICC 01-01-2009. Jan. 7, 2009. 

\item
      Francisco D. Igual, Gregorio Quintana-Ort\'{\i}, and Robert van de Geijn. "Level-3 BLAS on a GPU: Picking the Low Hanging Fruit " FLAME Working Note \#37. Universidad Jaume I, Depto. de Ingenieria y Ciencia de Computadores. Technical Report DICC 2009-04-01. April 30, 2009, Updated May 21, 2009.

\item
      Ernie Chan, Jim Nagle, Robert van de Geijn, and Field G. Van Zee. "Transforming Linear Algebra Libraries: From Abstraction to Parallelism." FLAME Working Note \#38. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-09-17. May 27, 2009. 

\item
      Ernie Chan. "Runtime Data Flow Scheduling of Matrix Computations." FLAME Working Note \#39. The University of Texas at Austin, Department of Computer Sciences. Technical Report TR-09-22. August 10, 2009. 
\end{enumerate}

\section{Other Technical Reports}

\renewcommand\labelenumi{R\theenumi}

\begin{enumerate}
\item
      Rosa M. Badia, Jose R. Herrero, Jesus Labarta, Josep M. Perez, Enrique S. Quintana-Ort\'{\i} and Gregorio Quintana-Orti. Parallelizing dense and banded linear algebra libraries using SMPSs. Departament of Computer Architecture, Universitat Politecnica de Catalunya. Technical Report UPC-DAC-RR-2008-64. 2008.
\item
Paolo Bientinesi and Robert van de Geijn. 
Automation in Dense Linear Algebra.
Aachen Institute for Computational Engineering Science, RWTH Aachen. Technical Report AICES-2008-2. October 2008.
\end{enumerate}

\renewcommand\labelenumi{\theenumi}
