
%The \libflame source code is available in two forms: the previous milestone
%release and the latest nightly snapshots.
%{\bf Milestones and nightly snapshots.}
%We encourage users to download and use the latest nightly snapshot.
%These packages contain full copies of the \libflame source tree, including
%all the relevant build system scripts and makefiles.
%Though it may seem like the milestone releases would be more stable and the
%nightly snapshots more prone to bugs, this is not really the case.
%Milestone releases are fine immediately after they are released, but they
%quickly grow out-of-date.
%It is more likely that the bugs present in the previous milestone release
%have been identified and fixed in the latest nightly snapshot.
%Furthermore, we do not offer any ``updates'' to milestone releases in
%between major versions.
%It is for this reason that we strongly encourage users to use the latest
%nightly snapshot, especially if you encounter problems compiling the
%source code.
The \libflame source code is available in two forms:
\begin{itemize}
\item
{\bf Nightly snapshots.}
We encourage users to download and use the latest nightly snapshot.
These packages contain full copies of the \libflame source tree, including
all the relevant build system scripts and makefiles as well as items of
interest to developers of \libflamens.
As their name suggests, these releases represent the state of the \libflame
repository each night (early morning, actually).
Expect these nightly snapshots to incorporate the latest interfaces,
code improvements, and bug fixes.
\item
{\bf Milestone releases.}
The \libflame team also makes previous milestone releases available to
users.
These releases are similar to the nightly snapshots, except that they are
also associated with an incremented version number and an update of the
\changelogns.
\end{itemize}
Though it may seem like the milestone releases would be more stable and the
nightly snapshots more prone to bugs, we have actually found the opposite
to be true.
Milestone releases are fine immediately after they are released, but they
quickly grow out-of-date.
%Users should be aware that by downloading an older milestone release, you
%may be downloading code with bugs that have already been fixed.
%Bugs are fixed as soon as possible after they are identified;
%however, it should be noted that these fixes are not applied as ``updates''
%to older releases
%Furthermore, it should be noted that we do not offer ``updates'' to
%milestone releases in between major versions.
%We try to fix bugs as soon as they are identified, however, these updates
%are not applied to older releases.
We check in updates to the library often, sometimes several times in one day.
However, these updates are not applied to older releases.
If an error exists in an older milestone release and the fix has already
been applied by \libflame developers, then the user must obtain
a more recent nightly snapshot to obtain the corrected code.\footnote{The user may also
find bug fixes by downloading a more recent milestone release.
However, since milestone releases are quite infrequent, roughly one per year,
obtaining a more recent milestone release is oftentimes not an option.}
It is for this reason that we {\em strongly} encourage users to use nightly
snapshots over milestones.

%If an error exists in an older release (milestone or nightly) and you suspect
%that the issue has not yet been addressed, please don't hesitate to contact
%the developers!
%You may email us anytime at \flameemailns.

%It is likely that a number of the bugs present in the previous milestone
%release have been identified and fixed in subsequent nightly snapshots.
%%It is for this reason that we strongly encourage users to use nightly
%%snapshots over milestones.%, especially if you encounter problems compiling the
%source code.
%Common problems such as errors while compiling code are likely to have
%already 

